Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-07-22 docs/paper/paper.Rmd
add  bullet S and T's

# Forecasts

@@

# Models with a single location target
locations_per_model <- metadata |>
    summarise_forecasts_by(var = "location", by = "model")

@@

#Varying submissions
varying_submissions <- locs_per_model_date |>
  DT(partial_models[, .(model)], on = "model")

# Models coverage of forecast datees
forecast_dates_by_models <- metadata |>
  summarise_forecasts_by(var = "target_end_date", by = "model") |>
  DT(order(n)) |>
  DT(, n_per := n / forecast_dates) |>
  DT(, type := fcase(
      model %in% global_models, "global",
      model %in% local_models, "local",
      model %in% partial_models[, model], "partial",
      default = "other"
    )
  )
```

@@

- Forecast performance overview for the ensemble and surrogate.
- Forecast performance overview by forecast horizon. Highlight degrading performance with this impacting the surrogate model to a greater degree. 
- Discussion country level differences in performance and link to potential growth rate trends.

@@

- Relative performance of surrogate model by forecast horizon.
   - Give mean relative performance difference by horizon
   - Discuss distribution.
- Relative performance of surrogate model by month stratified by forecast horizon.
  - Give mean relative performance by month for each horizon
  - Discuss distribution
- Relative performance of surrogate model by location sratified by forecast horizon.
  - Discuss qualatative differences between locations

@@

@@

Whilst we found that our surrogate model performed compab
  - Other similar model formulations. More lag terms. Reduced run-times using approximate Bayesian approaches.

>>>>

@@

# Models with a location target
locations_per_model <- metadata |>
    summarise_forecasts_by(var = "location", by = "model")

@@

# Varying submissions
varying_submissions <- locs_per_model_date |>
  DT(partial_models[, .(model)], on = "model")

# Models coverage of forecast dats
forecast_dates_by_models <- metadata |>
  summarise_forecasts_by(var = "target_end_date", by = "model") |>
  DT(order(n)) |>
  DT(, n_per := n / forecast_dates) |>
  DT(, type := fcase(
      model %in% global_models, "global",
      model %in% local_models, "local",
      model %in% partial_models[, model], "partial",
      default = "other"
    )
  )
```

@@

- Forecast performance overview for the ensemble and surrogate.
- Forecast performance overview by forecast horizon. Highlight degrading performance with this impacting the surrogate model to a greater degree. 
- Discussion country level differences in performance and link to potential growth rate trends. 
- Discuss differences between countries with different numbers and kinds of submitted forecast models.

@@

- Relative performance of surrogate model by forecast horizon.
   - Overall performance (mean)
   - Give mean relative performance difference by horizon
   - Discuss distribution.
- Relative performance of surrogate model by month stratified by forecast horizon.
  - Give mean relative performance by month for each horizon
  - Discuss distribution
- Relative performance of surrogate model by location sratified by forecast horizon.
  - Discuss qualatative differences between locations

@@

- Real-time evaluation of a model with development tracked using version control (showing no changes since January 2022).
- Conducted using reproducibility best practices with all code available for reuse. THe model is implemented in GitHub actions so can be reused without any compute resources and is by definition fast to run.
- Only use absolute scoring which has implications for what we consider a good model. This is the approach used by the hub and so makes sense here but area of active research to understand what is more appropriate.
- Limited exploration of model formulations. Likely that there are alternatives that perform closer to the ensemble
- As our target is not to produce the best COVID-19 forecast model, or the best COVID-19 forecast model as defined using the metrics used to evaluate by the ECDC but rather to develop a model that closely matches the Hub ensemble whilst maintaining interpretability and using limited resources it is likely that it will perform less  well than a forecast model designed with the first two criterion in mind. 
  - However, if we start from the review that the forecast hub ensemble has traits that are desirable for use by policy-makers (i.e robustness and good average performance) then our approach makes sense. This is the view often used in the literature.

@@

Whilst we found that our surrogate model performed compab
  - Other similar model formulations. More lag terms. Reduced run-times using approximate Bayesian approaches.
  - Role of simple models for adjusting for susceptible population. Highlight useful now but not in early pandemic
  - Follow up study comparing these results to retrospective forecasts from early in the pandemic or on other infectious disease outbreaks (though limited by requirement of a multi-team ensemble to compare to).
